POMDP comparisons across sigma_m, sigma_g

### 2017-10-11 appendix/appendixB.Rmd
tweaking fig

             ## FIXME need to get obs for unique commmonname, wrong length?
             who <- (ex$commonname == meta[.z,"commonname"]) 
             df <- ex[who,]

@@

```{r}
sims %>%
  filter(model %in% c("biomass", "catch", "pomdp_0.2", "reed", "pgy")) %>%
  ggplot(aes(year, stock, col=model)) +
  geom_line(lwd=1) +
  scale_color_manual(values = c("black", "grey", "#D9661F", "#FDB515", "#6C3302", "#00B0DA", "#CFDD45", "#3B7EA1")) +
  facet_wrap(~commonname, scales = "free", ncol=1) + theme_bw()  
```

>>>>

             ## avoid NSE
             who <- (ex$commonname == meta[.z,"commonname"]) 
             df <- ex[who,]

@@

```{r}
sims %>%
  filter(model %in% c("biomass", "catch", "pomdp_0.1", "reed", "pgy")) %>%
  ggplot(aes(year, stock, col=model)) +
  geom_line(lwd=1) +
  scale_color_manual(values = c("black", "grey", "#D9661F", "#3B7EA1", "#FDB515", "#6C3302",  "#00B0DA",  "#CFDD45")) +
  facet_wrap(~commonname, scales = "free", ncol=1) + theme_bw()  
```
